### 2021-09-01 README.Rmd
Modify variables and data frames.

-  `wages_hs`: The wages data from the cohort whose highest grade completed is up to 12th grade.
-  `wages_hs_do`: The wages data of the high school dropouts.
-  `demog_nlsy79`: The demographic data of the NLSY79 cohort.

@@

ggplot(wages_hs, 
       aes(x = year,
                y = mean_hourly_wage,
                group = id)) +
  geom_line(alpha = 0.7) +
  facet_sample() +
  ylab("mean hourly wage") +
  theme_bw()
```

>>>>

-  `wages`: The wages data from the cohort whose highest grade completed is up to 12th grade.
-  `wages_hs_do`: The wages data of the high school dropouts.
-  `demog_nlsy79`: The demographic data of the NLSY79 cohort.

@@

ggplot(yowie::wages, 
       aes(x = year,
           y = wage,
           group = id)) +
  geom_line(alpha = 0.7) +
  facet_sample() +
  ylab("mean hourly wage") +
  theme_bw()
```
